\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-30 paper.qmd
Update the views with true model

<!--langevitour with pD model for S-curve-->
::: {#fig-scurve-sc layout-ncol="4" fig-pos="H"}
![](figures/scurve/umap_view_copy.png)

@@

XXX Model in \gD{}, on the UMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape, but it has breaks which means that it does not adequately capture the surface. (The **langevitour** software is used to view the data with a tour, and the full video is available at (<https://youtu.be/G1m4q9k--v4>). NEED TO CHANGE FIRST PLOT TO BE 2D WIREFRAME.
:::

>>>>

<!--langevitour with pD model for S-curve-->
::: {#fig-scurve-sc layout-ncol="4" fig-pos="H"}
![](figures/scurve/sc_best_trimesh.png)

@@

XXX Model in \gD{}, on the UMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape, but it has breaks which means that it does not adequately capture the surface. (The **langevitour** software is used to view the data with a tour, and the full video is available at (<https://youtu.be/N6iWEj3aVps>). 
:::

### 2024-06-30 paper.tex
Update the views with true model

\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/umap_view_copy.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_1.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_2.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_3.png}\end{minipage}%

\caption{\label{fig-scurve-sc}XXX Model in \gD{}, on the UMAP layout,
and three views of the fit in projections from \(7\text{-}D\), for the
S-curve data. The model closely fits the shape, but it has breaks which
means that it does not adequately capture the surface. (The
\textbf{langevitour} software is used to view the data with a tour, and
the full video is available at (\url{https://youtu.be/G1m4q9k--v4}).
NEED TO CHANGE FIRST PLOT TO BE 2D WIREFRAME.}

>>>>

\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_best_trimesh.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_1.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_2.png}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/scurve/sc_3.png}\end{minipage}%

\caption{\label{fig-scurve-sc}XXX Model in \gD{}, on the UMAP layout,
and three views of the fit in projections from \(7\text{-}D\), for the
S-curve data. The model closely fits the shape, but it has breaks which
means that it does not adequately capture the surface. (The
\textbf{langevitour} software is used to view the data with a tour, and
the full video is available at (\url{https://youtu.be/N6iWEj3aVps}).}
